Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-01-19 paper.tex
RQ1: Draft of enlarged Table 1

\begin{table}
\caption{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.}
\centering
\begin{tabular}{ccc}
&
$\eta=10^{-4}$ &
$\eta=10^{-3}$ \\
\midrule
Theoretical average linear growth rate of flute $\gamma$ & 0.86 & 1.79  \\
Observed nonlinear growth rate of flute $\gamma$ & 0.69 & 1.06  \\
Observed growth rate of kink $\lambda$ & 2.55 & 0.15\\
\midrule
Theoretical radius $r_s$ of peak flute growth rate & 0.125 & 0.163 \\
Observed radius $r_s$ of peak flute growth rate & 0.125 & 0.163 \\
\midrule
Observed axial wave number $k_{\text{flute}}$ & 23.61 & 16.05 \\
Observed axial wave number $k_{\text{kink}}$ & 4.57 & 4.53 \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table}

@@

@@

The growth rate of the kink instability is, counter-intuitively, lower in the
weakly dissipative anisotropic cases, compared to the strongly dissipative
isotropic cases, i.e. one would expect the kink instability to grow more
quickly (or at least be unaffected) when using anisotropic viscosity. Indeed,
the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
this behaviour, where the kink instability grows (marginally) faster in the
anisotropic cases. We speculate that it is the presence of the flute modes which
negatively affects the growth of the kink instability.} {It seems unlikely that
in the linear regime the perturbations of the flute and kink are able to
directly couple, given that the kink instability generally presents at the axis
of a flux tube and the flute at some resonant surface away from the
axis.} \rev{Instead of a linear coupling, we believe that the linear kink instability is
disturbed by the more complex magnetic field configuration that arises due to
the mixing caused by the nonlinear development of the flute modes. The
complexity in the field can be seen by comparing
figures~\ref{fig:field_line_plots_iso} and~\ref{fig:field_line_plots_swi}.

>>>>

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{\rev{Anisotropic}}& \multicolumn{2}{c}{\rev{Isotropic}} \\
&
$\eta=10^{-4}$ &
$\eta=10^{-3}$ &
\rev{$\eta=10^{-4}$} &
\rev{$\eta=10^{-3}$} \\
\midrule
Theoretical average linear growth rate of flute $\gamma$ & 0.86 & 1.79
& \rev{??} & \rev{??} \\
Observed nonlinear growth rate of flute $\gamma$ & 0.69 & 1.06  &
\rev{--} & \rev{1.06}\\
Observed growth rate of kink $\lambda$ & 2.55 & 0.15 & \rev{2.97} & \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak flute growth rate & 0.125 & 0.163 &
\rev{--} & \rev{??}\\
Observed radius $r_s$ of peak flute growth rate & 0.125 & 0.163 & \rev{--} & \rev{??}\\
\midrule
Observed axial wave number $k_{\text{flute}}$ & 23.61 & 16.05 & \rev{--} & \rev{??} \\
Observed axial wave number $k_{\text{kink}}$ & \rev{??} & \rev{??} & 4.57 & 4.53\\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}

@@

\rev{Perturbing a magnetic flux tube by dynamic twisting of the flow
at the cylinder bases leads to excitation of the flute instability in
addition to the well studied kink instability.}

@@

The growth rate of the kink instability is, counter-intuitively, lower in the
weakly dissipative anisotropic cases, compared to the strongly dissipative
isotropic cases, i.e. one would expect the kink instability to grow more
quickly (or at least be unaffected) when using anisotropic viscosity. Indeed,
the simulations reported in~\citet{quinnEffectAnisotropicViscosity2020} display
this behaviour, where the kink instability grows \newold{}{(marginally)} faster in the
anisotropic cases. We speculate that it is the presence of the flute modes which
negatively affects the growth of the kink instability.} {It seems unlikely that
in the linear regime the perturbations of the flute and kink are able to
directly couple, given that the kink instability generally presents at the axis
of a flux tube and the flute at some resonant surface away from the
axis.} \rev{We believe that, instead of a linear coupling, the linear kink instability is
disturbed by the more complex magnetic field configuration that arises due to
the mixing caused by the nonlinear development of the flute modes. The
complexity in the field can be seen by comparing
figures~\ref{fig:field_line_plots_iso} and~\ref{fig:field_line_plots_swi}.
